### 2024-02-18 documentation/thesis/thesis_abstract.tex
.

A passive shimming process is typically used to adjust the field
afterwards. This is complex and time-consuming and requires manual
corrections to the magnets used. To avoid this process, magnets can be
systematically measured in advance. Sensor accuracy and repeatability
Data acquisition, storage and subsequent analysis play an important role
in this methodology.

>>>>

A passive shimming process is typically used to adjust the B0 field
afterwards. This is complex and time-consuming and requires manual
corrections to the magnets used. To avoid this process, magnets can be
systematically measured in advance. Sensor accuracy and repeatability
data acquisition, storage and subsequent analysis play an important role
in this methodology.

### 2024-02-18 documentation/thesis/thesis_document.tex
.

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at various locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open-source software for this thesis is designed
not only to facilitate measurements with different sensors but also to
enable the characterisation of different objects.

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring. In this generated model eight
cubic \emph{12x12x12mm} magnets are embedded to generate homogeneous
magnetic flux densities of around \emph{20mT}. The homogeneity in this
configuration depends, among other things, on the following main
aspects:

@@

The application of the develox field sensors serve the practical
application and validation of the developed solution.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which can measure diverse objects using various sensors.
Additionally, remarks need to be provided regarding the suitability of
the employed sensors for magnetic field measurements.

@@

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}.

All parts are produced using 3D printing additive manufacturing process.
The sensor circuit board is glued underneath the magnet holder. This is
interchangeable, so different distances between sensor and magnet can be
realised. The exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspeaction whether
the hardware is working properly after firmware installation. The
command \emph{help}, displays a detailed command reference wit all
available commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user. The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

Once the hardware has been prepared, the task of the firmware of the
various sensors is to find a common synchronisation clock. The figure
\ref{Unified_sensor_fiUnified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.pngrmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
shows how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The firmware-function
\emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors equipped with different sensor \gls{ic}s
to cover various magnet charaterisation setups
\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-fullsphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

This allows the host to address individual sensors directly via their
specific \gls{uuid} and extendet id parameter.

@@

The various steps are linked by using the \emph{stage } macro as input
parameter of the next function to be executed (see comments in listing
\ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to use the
results of one function in several others without them directly
following each other. The disadvantages of this system are the
following:

@@

To determine the order of the pipeline steps, the parser script created
converts them into one problem of the graph theories. Each step
represents a node in the graph and the steps referred to by the input
parameter form the edges. After several simplification steps,
determination of start steps and repeated traversal, the final execution
sequence can be determined in the form of a call tree in figure
\ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
The individual steps are then executed along the graph. The intermediate
results and the results in figure
\ref{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
are saved for optional later use.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}
\caption{Pipeline output files after running example pipeline on a set
of readings
\label{Pipeline_output_files_after_running_example_pipeline_on_a_set_of_readings.png}}
\end{figure}

@@

\begin{lstlisting}[language=Python, caption={Example pytest class for testing MRPReading module functions}, label=lst:pytest_example_code]
class TestMPRReading(unittest.TestCase):
  # PREPARE AN INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
  def setUp(self) -> None:
    self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
    self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")

@@

\hypertarget{haluation}{%
\chapter{Haluation}\label{haluation}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Ten_numbered_test_magnets_in_separate_holders.png}
\caption{Ten numbered test magnets in separate holders
\label{Ten_numbered_test_magnets_in_separate_holders.png}}
\end{figure}

For the hardware setup, the 3D-Full Sphere sensor, explained in chapter
\ref{d-full-sphere}, is used for the evaluation of the framework. As
this is equipped with an exchangeable magnetic holder mount, suitable
holders are required for the magnets to be measured. Ten random
\emph{N45 12x12x12mm} neodymium magnets are used, which are shown in
figure \ref{Ten_numbered_test_magnets_in_separate_holders.png}.

These are placed in modified 3D printed holders shown in figure
\ref{Ten_numbered_test_magnets_in_separate_holders.png} and afterwards
numbered. This allows to match the magnets to the measurement results
later.

@@

Once the filter function has been implemented, it still needs to be
integrated into the analysis pipeline in listing
\ref{lst:pipeline_mrp_evaluation_yaml}. At this point, he example
pipeline in figure \ref{Example_measurement_analysis_pipeline.png} is
simplified and an additional stage \emph{find\_similar\_values} has been
added, which has set \emph{FindSimilarValuesAlgorithm} as the function
to be called. As a decisive step, the result is used in the
\emph{plot\_filtered} stage for visualisation.

\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm}, label=lst:pipeline_mrp_evaluation_yaml]
settings:
  enabled: true
  export_intermediate_results: false
  name: pipeline_mrp_evaluation

@@

The figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
summarizes this result. The plot of the raw measured values is
represented on the left. The value of the determined \emph{GoG} \(\mu\)T
values is plotted on ten individual measured values. It can be seen that
there are measured values with larger deviations (see measurement
\emph{7:0},\emph{10-2:0},\emph{10-1:0}).

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensors internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

@@

With this version of the framework, a solid basis has been created that
contains all the necessary functions to solve various problems in the
acquisition and processing of magnetic fields. Easy-to-assemble
measurement hardware has created an easy-to-use platform for the
characterisation of permanent magnets, for example. An exemplary
characterisation of the magnetic field sensors used allows the possible
areas of application for these to be narrowed down. The framework has
already been published in a first stable version, but extensions and
improvements are still necessary. The stable version is also distributed
via a package registration and can therefore be quickly evaluated by new
users. In addition, further user experience and actual measurements
under real laboratory conditions on \gls{mri} B0 field magnets are still
missing. This is limited by the currently restricted selection of
characterised sensors. The aim for the next revision of the hardware and
software framework is therefore to support additional magnetic field
sensors. The current restriction to purely digital sensor interfaces is
also to be extended to analogue interfaces. This will open up the use of
a wide range of magnetic field sensors. It is also possible to integrate
high-resolution magnetic field probes based onNMR samples, which can
cover measurement errors of less than \emph{10nT} in fields of more than
\emph{1T} \customcite{DBN08}. Another possibility already supported by the
software, but for which hardware development is still necessary, is 2D
arrays of magnetic field sensors to display fields on a
surface\customcite{CP16}. This means that deviations can also be
visualised graphically without physically moving the senso such as in
the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
addition, larger areas or volumes, such as in a large \emph{B0} field,
can be measured more quickly.

>>>>

To address this challenge, the thesis proposes the development of a
comprehensive hardware and software framework. The hardware system aims
to selectively measure magnetic fields at various locations or fully
around a permanent magnet using different sensors. Several existing
open-source software solutions implement individual parts, but do not
provide a complete data processing pipeline from acquisition to
analysis, and their data storage formats are not compatible with each
other. The accompanying open source software for this work is not only
designed to enable measurements with various sensors, but also to
characterise permanent magnets, magnetic fields and the sensors
themselves.

@@

A Halbach ring of this type is usually based on a ring with permanent
magnets arranged in a circle. The figure
\ref{Example_Halbach_ring_with_cutouts_for_eight_magnets.png} shows an
example \gls{cad} model of such a ring.

In this generated model eight cubic \emph{12x12x12mm} magnets are
embedded to generate homogeneous magnetic flux densities of around
\emph{20mT}. The homogeneity in this configuration depends, among other
things, on the following main aspects:

@@

The characterisation of field sensors in consumer quality serves the
practical application and validation of the developed solution.

@@

Finally, a comprehensive hardware and software framework needs to be
established, which can measure diverse objects using various sensors. In
addition, comments must be made on the suitability of the sensors used
for magnetic field measurements.

@@

Figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png},
shows rendered view of the 1D-Single sensor \gls{cad} drawing, which is
described in chapter \ref{d-single-sensor}. All parts are produced using
3D printing additive manufacturing process. The sensor circuit board is
glued underneath the magnet holder. This is interchangeable, so
different distances between sensor and magnet can be realised. The
exchangeable magnetic holder (shown in green in figure
\ref{Rendered_mechanical_structure_of_the_1D_sensor_(+cad)_model_with_different_parts_colored_separately,_and_universal_magnet_mount_shown_in_green.png})
can be adapted to different magnets. It can be produced quickly due to
the small number of parts used. The two recesses lock the magnet holder
with the inserted magnet over the sensor. The specified tolerances allow
the magnet to be inserted into the holder with repeat accuracy and
without backlash. This is important if several magnets must be measured,
where the positioning over the sensor must always be the same.

@@

The \gls{cli} mode is a simple text-based interface with which it is
possible to read out current measured values, obtain debug information
and set operating parameters. This allows to quickly inspect whether the
hardware is working properly after firmware installation. The command
\emph{help}, displays a detailed command reference with all available
commands as shown in the figure
\ref{Unified_sensor_firmware_provided_serial_terminal_based_(+cli)_allows_the_user_to_configure_the_sensor_manually.png}
to the user. The figure
\ref{Result_of_an_executed_b_value_measurement_readout_command_using_the_sensors_(+cli)_with_immediate_user_readable_response.png}
shows the current measured value queried by using the \emph{readout}
command by the user.

@@

Once the hardware has been prepared, the task of the firmware of each of
the chained sensors is to find a common synchronisation clock. The
figure
\ref{Unified_sensor_firmware_multi_sensor_synchronisation_procedure_using_sync_(+gpio)_input_for_operation_(primary_or_secondary)_mode_decision.png}
illustrates how the firmware handles the decision task if the sensor is
\emph{primary} or \emph{secondary} at startup. The firmware-function
\emph{register irq on sync pin} is overwritten. To set one
\emph{primary} and several \emph{secondary} sensors, each sensor waits
for an initial pulse on the SYNC-\gls{gpio}, which is a pin at the
microcontroller with the functionality to detect if the sensor is a
primary or a secondary sensor. A random timer is started beforehand by
each sensor, which sends a pulse on the sync line. All others receive
this and switch to \emph{secondary mode} and synchronise the
measurements based on each sync pulse received.

@@

\begin{longtable}[]{@{}llll@{}}
\caption{Build hardware sensors equipped with different sensor \gls{ic}s
to cover various magnet charaterisation setups
\label{Build_hardware_sensors_equipped_with_different_sensor_(+ic)s_to_cover_various_magnet_charaterisation_setups.csv}}\tabularnewline
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-full-sphere}\tabularnewline
\midrule
\endfirsthead
\toprule
& 1D\ref{d-single-sensor} & 1D: dual sensor & 3D:
Fullsphere\ref{d-full-sphere}\tabularnewline
\midrule
\endhead
Maximal magnet size & Cubic 30x30x30mm & Cubic 30x30x30mm & Cubic
20x20x20mm\tabularnewline
Sensor type & MMC5603NJ & TLV493D & TLV493D\tabularnewline
Sensor count & 1 & 2 & 1\tabularnewline
Scanmode & static (1 point) & static (2 points) & dynamic
(fullsphere)\tabularnewline
\bottomrule
\end{longtable}

@@

This allows the host to address individual sensors directly via their
specific \gls{uuid} and extended id parameter.

@@

The various steps are linked by using the \emph{stage NAME} macro as
input parameter of the next function to be executed (see comments in
listing \ref{lst:mrpuddp_example_yaml}). Therefore, it is feasible to
use the results of one function in several others without them directly
following each other. The disadvantages of this system are the
following:

@@

To determine the order of the pipeline steps, the parser script created
converts them into one problem of the graph theories. Each step
represents a node in the graph and the steps referred to by the input
parameter form the edges. After several simplification steps,
determination of start steps and repeated traversal, the final execution
sequence can be determined in the form of a call tree in figure
\ref{Example_result_of_an_step_execution_tree_from_user_defined_processing_pipeline.png}.
The individual steps are then executed along the graph. The intermediate
results and the results in figure
\ref{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}
are saved for optional later use.

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}
\caption{Generated pipeline output files and example results combined
into one plot after running example pipeline on a set of readings
\label{Generated_pipeline_output_files_and example_results_combined_into_one_plot_after_running_example_pipeline_on_a_set_of_readings.png}}
\end{figure}

@@

\begin{lstlisting}[language=Python, caption={Example of a PyTest class for testing the internal functions of the MRPReading and MRPSimulation modules}, label=lst:pytest_example_code]
class TestMPRReading(unittest.TestCase):
  # PREPARE AN INITIAL CONFIGURATION FILE FOR ALL FOLLOWING TEST CASES IN THIS FILE
  def setUp(self) -> None:
    self.test_folder: str = os.path.join(os.path.dirname(os.path.abspath(__file__)), "tmp")
    self.test_file:str = os.path.join(self.import_export_test_folderpath, "tmp")

@@

\hypertarget{use-case-evaluation}{%
\chapter{Use Case Evaluation}\label{use-case-evaluation}}

@@

\begin{figure}
\centering
\includegraphics{./generated_images/border_Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}
\caption{Ten numbered N45 12x12x12mm test magnets in separate 3D printed
holders
\label{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}}
\end{figure}

For the hardware setup, the 3D-Full Sphere sensor, explained in chapter
\ref{d-full-sphere}, is used for the evaluation of the framework. As
this is equipped with an exchangeable magnetic holder mount, suitable
holders are required for the magnets to be measured. Ten random
\emph{N45 12x12x12mm} neodymium magnets are used, which are shown in
figure
\ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}.

These are placed in modified 3D printed holders shown in figure
\ref{Ten_numbered_N45_12x12x12mm_test_magnets_in_separate_3D_printed_holders.png}
and afterwards numbered. This allows to match the magnets to the
measurement results later.

@@

Once the filter function has been implemented, it still needs to be
integrated into the analysis pipeline in listing
\ref{lst:pipeline_mrp_evaluation_yaml}. At this point, the example
pipeline in figure \ref{Example_measurement_analysis_pipeline.png} is
simplified and an additional stage \emph{find\_similar\_values} has been
added, which has set \emph{FindSimilarValuesAlgorithm} as the function
to be called. As a decisive step, the result is used in the
\emph{plot\_filtered} stage for visualisation.

\begin{lstlisting}[caption={User defined processing pipeline using custom implemented filter algorithm in third stage}, label=lst:pipeline_mrp_evaluation_yaml]
settings:
  enabled: true
  export_intermediate_results: false
  name: pipeline_mrp_evaluation

@@

The figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}
summarizes this result. The plot of the raw measured values is
represented on the left. The value of the determined \emph{GoG} \(\mu\)T
values is plotted on ten individual measured values. It can be seen that
there are measured values with larger deviations (see measurement plots
\emph{7:0},\emph{10-2:0},\emph{10-1:0} in figure
\ref{MRP_evaluation_result_after_find_similar_values_algorithm_execution_in_the_user_defined_pipeline.png}).

@@

\begin{itemize}
\tightlist
\item
  Plot of the raw data of the sensor
\item
  Plot of the sensor's internal temperature sensor
\item
  Background noise level with reference to the initial baseline
\item
  Histogram of the background noise level
\end{itemize}

@@

With this version of the framework, a solid basis has been created that
contains all the necessary functions to solve various problems in the
acquisition and processing of magnetic fields. Easy-to-assemble
measurement hardware has created an easy-to-use platform for the
characterisation of permanent magnets, for example. An exemplary
characterisation of the magnetic field sensors used allows the possible
areas of application for these to be narrowed down. The framework has
already been published in a first stable version, but extensions and
improvements are still necessary. The stable version is also distributed
via a package registration and can therefore be quickly evaluated by new
users. In addition, further user experience and actual measurements
under real laboratory conditions on \gls{mri} B0 field magnets are still
missing. This is limited by the currently restricted selection of
characterised sensors. The aim for the next revision of the hardware and
software framework is therefore to support additional magnetic field
sensors. The current restriction to purely digital sensor interfaces is
also to be extended to analogue interfaces. This will open up the use of
a wide range of magnetic field sensors. It is also possible to integrate
high-resolution magnetic field probes based on NMR samples, which can
cover measurement errors of less than \emph{10nT} in fields of more than
\emph{1T} \customcite{DBN08}. Another possibility already supported by the
software, but for which hardware development is still necessary, is 2D
arrays of magnetic field sensors to display fields on a
surface\customcite{CP16}. This means that deviations can also be
visualised graphically without physically moving the senso such as in
the implemented \emph{3D: Full Sphere} \ref{d-full-sphere} sensor. In
addition, larger areas or volumes, such as in a large \emph{B0} field,
can be measured more quickly.
